---
title: "P8105 Homework 5"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


## Problem 1

The code chunk below imports the data in individual spreadsheets contained in `./data/zip_data/`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = subj)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 


## Problem 2
```{r}
homicide_data = read_csv("./data/homicide_data.csv")

homicide_data
```

This raw dataset contains `r nrow(homicide_data)` rows and `r ncol(homicide_data)` columns. Important variables include date, state, city, disposition, and information about victims such as race, age, sex, and names, etc. Each raw represents one single homicide case.

Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r}
homicide = homicide_data %>% 
  mutate(
    city_state = str_c(city, ', ', state)
  )

total_num = homicide %>% 
  group_by(city_state) %>% 
  summarize(
    total = n(),
  )

unsolved_num = homicide %>% 
  filter(disposition %in% c("Closed without arrest", "Open/No arrest")) %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = n()
  )

summary = inner_join(unsolved_num, total_num, by = "city_state")
```


For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object.


```{r}
Baltimore_test = summary %>% 
  filter(city_state == "Baltimore, MD")

Baltimore_test =  
  prop.test(Baltimore_test[["unsolved"]], Baltimore_test[["total"]]) %>% 
  broom::tidy()
```

Pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
Baltimore_test %>% 
  select(estimate, conf_low = conf.low, conf_high = conf.high) %>% 
  knitr::kable()
```

Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

Firstly, write a function:

```{r}
city_test = function(df) {
  
    prop.test(df[["unsolved"]], df[["total"]]) %>% 
    broom::tidy() %>% 
    select(estimate, conf_low = conf.low, conf_high = conf.high)
  
}
```

Apply this function to the `summary` dataframe:

```{r}
test_outcome = 
  summary %>% 
  nest(unsolved:total) %>% 
  mutate(
    outcome = map(data, city_test)
  ) %>% 
  unnest(outcome) %>% 
  select(-data)

head(test_outcome) %>% 
  knitr::kable()
```

Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

```{r}
test_outcome %>% 
  mutate(
    city_state = fct_reorder(city_state, estimate)
  ) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high)) +
  theme(axis.text.x = element_text(
      angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    title = "Proportion of Unsolved Homicides for Each City",
    x = "City",
    y = "proportion"
  )
```

According to this plot, Richmond has the lowest proportion of unsolved homicides, while Chicago has the highest.


## Problem 3
First set the following design elements:

* Fix n=30

* Fix σ=5

Set μ = 0. Generate 5000 datasets from the model x ∼ Normal[μ,σ].

For each dataset, save μ̂ and the p-value arising from a test of H:μ=0 using α=0.05.

First write a function:

```{r}
sim_t_test = function(true_mean) {
  sample = rnorm(30, mean = true_mean, sd = 5)
  
  t.test(sample) %>% 
    broom::tidy() %>% 
    select(estimate, p_value = p.value)
}
```

Set μ = 0. Generate 5000 datasets from the model x ∼ Normal[μ,σ].

```{r}
sim_results_df1 = 
  expand_grid(
    mu = 0,
    iteration = 1:50
  ) %>% 
  mutate(
    result = map(mu, sim_t_test)
  ) %>% 
  unnest(result)

sim_results_df1
```

Repeat the above for μ={1,2,3,4,5,6}:
```{r}
sim_results_df2 = 
  expand_grid(
    mu = 1:6,
    iteration = 1:50
  ) %>% 
  mutate(
    result = map(mu, sim_t_test)
  ) %>% 
  unnest(result) 

head(sim_results_df2)
```


* Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.

```{r}
sim_results_df2 %>% 
  group_by(mu) %>% 
  mutate(
    reject = ifelse(p_value < 0.05, TRUE, FALSE),
    power = mean(reject)
  ) %>% 
  ggplot(aes(x = mu, y = power)) +
  geom_point() +
  labs(
    title = "The Association Between Effect Size and Power",
    x = "True Mean",
    y = "Power"
  )
```

According to the plot, as true value of μ increases, the proportion of times the null (μ=0) was rejected (the power of the test) is also increasing. It shows that effect size and power are positively associated.